\documentclass[11pt]{article}

\usepackage[letterpaper,margin=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlist[itemize]{leftmargin=1.2em, itemsep=0.2em, topsep=0.25em}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.6em}{0.35em}

\newcommand{\resumeentry}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3}%
  \if\relax\detokenize{#4}\relax
  \else
    \hfill \textit{#4}%
  \fi
}

\begin{document}

\begin{center}
  {\LARGE \textbf{John Gilbert}} \\
  \vspace{0.2em}
  Software Developer \\
  \vspace{0.2em}
  Las Cruces, New Mexico \textbar\ 
  \href{tel:15754053364}{575-405-3364} \textbar\ 
  \href{mailto:jmgilbert23@gmail.com}{jmgilbert23@gmail.com} \textbar\ 
  \href{https://johnmgilbert.github.io}{johnmgilbert.github.io}
\end{center}

Software developer and computer science master's student building full-stack applications, data-driven tools, and technical analysis workflows. Brings a practical background in AI evaluation, analytical problem-solving, and cross-disciplinary collaboration, with a strong interest in software engineering and technical systems.

\section*{Technical Skills}
\textbf{Languages:} Python, JavaScript, C, C++, HTML, CSS \\
\textbf{Tools \& Platforms:} Pandas, Polars, NetworkX, Git, JSON \\
\textbf{Focus Areas:} Full-stack development, network analysis, data analysis \\
\textbf{Methods:} Feature engineering, model evaluation, workflow design, content moderation

\section*{Selected Projects}
\resumeentry{Animation Builder for Godot}{\href{https://johnmgilbert.github.io/pages/project/hcc.html}{Project page}}{Workflow tooling project}{}
\begin{itemize}
  \item Built a Godot-based asset and animation management tool to help artists and non-programmers work with imported assets through a clearer visual workflow.
  \item Implemented drag-and-drop importing, metadata organization, timeline-based frame sequencing, audio synchronization, and JSON export for downstream Godot integration.
  \item Ran two rounds of user studies with six participants each and used the feedback to improve layout clarity, export understanding, and task completion consistency.
\end{itemize}

\resumeentry{Food Waste Reducer AI}{\href{https://johnmgilbert.github.io/pages/project/seniorProj.html}{Project page}}{Research project}{}
\begin{itemize}
  \item Developed a proof-of-concept approach for reducing household perishable food waste through decentralized decision systems.
  \item Explored reward sharing across item-level Markov Decision Processes combined with Monte Carlo Tree Search to model realistic pantry planning behavior.
  \item Used repeated simulation results to evaluate how shared rewards could lower waste while preserving practical household constraints.
\end{itemize}

\resumeentry{Network Traffic Analysis}{Python, data analysis, NetworkX}{Network analysis and intrusion detection project}{}
\begin{itemize}
  \item Built a reproducible Python analysis pipeline for the FLNET2023 dataset covering router-topology reconstruction, unsupervised attack discovery, and supervised intrusion classification.
  \item Processed large router-flow datasets with Pandas, Polars, and PyArrow; engineered network-behavior features; and evaluated clustering workflows with UMAP, HDBSCAN, MiniBatchKMeans, and Gaussian Mixture models.
  \item Trained and evaluated multi-class intrusion-detection models with imbalance-handling strategies.
\end{itemize}

\section*{Experience}
\resumeentry{TELUS International}{Aug 2022 -- Present}{Internet Safety Evaluator}{Remote}
\begin{itemize}
  \item Evaluate online content against safety and quality guidelines to support moderation, trust and safety, and AI-related data workflows.
  \item Apply consistent judgment in high-volume review environments where policies and edge cases change over time.
  \item Strengthen analytical accuracy and attention to detail through independent review, policy interpretation, and documentation-focused work.
\end{itemize}

\resumeentry{Freelance Contractor}{Jan 2023 -- Present}{Residential projects}{Las Cruces, NM}
\begin{itemize}
  \item Manage small client projects including home repairs, renovation support, landscaping, and general handyman work.
  \item Coordinate project scope, materials, scheduling, and execution while working independently and maintaining client trust.
  \item Bring practical problem-solving, adaptability, and craftsmanship to projects with changing requirements and real-world constraints.
\end{itemize}

\resumeentry{Bakehouse LLC}{Jan 2013 -- Jun 2018}{Person in Charge}{Las Cruces, NM}
\begin{itemize}
  \item Oversaw daily bakery operations, food preparation, and catering support in a fast-paced production environment.
  \item Supervised employees, helped coordinate workflow, and maintained quality and consistency under deadline-driven conditions.
  \item Built leadership, training, and communication skills that continue to shape a calm and reliable approach to team-based work.
\end{itemize}

\section*{Education}
\resumeentry{New Mexico State University}{Aug 2024 -- Expected May 2026}{M.S. in Computer Science}{}
Current GPA: 3.9

\resumeentry{New Mexico State University}{Aug 2021 -- May 2024}{B.S. in Computer Science}{}
GPA: 3.9

\end{document}
